Estimating epidemiological quantities from repeated cross-sectional prevalence measurements

### 2022-02-15 writeup/paper.Rmd
add authors

---
title: "Estimating epidemiological quantities from repeated cross-sectional prevalence measurements"
bibliography: references.bib
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/apa.csl
date: "`r format(Sys.Date(), format = '%B %d, %Y')`"
output:
  bookdown::pdf_document2:
    toc: false
  bookdown::html_document2: default
---

>>>>

---
title: "Estimating epidemiological quantities from repeated cross-sectional prevalence measurements"
author: Sam Abbott, Sebastian Funk
bibliography: references.bib
csl: https://raw.githubusercontent.com/citation-style-language/styles/master/apa.csl
date: "`r format(Sys.Date(), format = '%B %d, %Y')` - WORK IN PROGRESS DRAFT"
output:
  bookdown::pdf_document2:
    toc: false
  bookdown::html_document2: default
---
